\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-31 paper.qmd
Updated version for the discussion
Add error calculations

We define the function $z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}$.

For the $i^{th}$ point, $z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(2)}_{jv})^2}$, and assign it to $H_h = \{i| z(i) = h\}$. Then, the fitted values for $i$ are defined as $C_{h}^{(2)} = (c_{h1}, c_{h2})$.

@@

To assess how well our method captures and represents the underlying structure of the \pD{} data, residuals are important. Residuals are computed by taking the squared \pD{} Euclidean distance, $\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{hj})^2$. Additionally, Mean Squared Error (MSE), $\frac{1}{n}\sum_{i = 1}^{n}\sum_{j = 1}^{p}(x_{ij} - C^{(p)}_{hj})^2$, is computed based on residuals.

@@

### Illustration on simulated data

>>>>

<!-- We define the function $z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}$, -->

<!-- For the $i^{th}$ point, $z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(2)}_{jv})^2}$, and assign it to $H_h = \{i| z(i) = h\}$. Then, the fitted values for $i$ are defined as $C_{h}^{(2)} = (c_{h1}, c_{h2})$.  -->

The fitted values refers to the \pD{} mappings of the \kD{} model.

@@

To assess how well our method captures and represents the underlying structure of the \pD{} data, residuals are important. Residuals are computed by taking the squared \pD{} Euclidean distance, $\sum_{h = 1}^{b}\sum_{i = 1}^{n_h}\sum_{j = 1}^{P} (x_{hij} - C^{(p)}_{hj})^2$. Additionally, Mean Squared Error (MSE), $\frac{1}{n}\sum_{h = 1}^{b}\sum_{i = 1}^{n_h}\sum_{j = 1}^{P} (x_{hij} - C^{(p)}_{hj})^2$, is computed based on residuals.

### Prediction

The prediction approach involves finding the nearest \kD{} model point for a new \pD{} point. We define the function $z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}$, where $z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(p)}_{jv})^2}$ maps each \pD{} point to its nearest \pD{} mapping of the model. Therefore, the new observation $i$ falls in the hexagon, $H_h = \{i| z(i) = h\}$ and the corresponding \kD{} bin centroids, $C_{h}^{(2)} = (c_{h1}, c_{h2})$ be the predicted values.

@@

## Deciding on the most suitable fit

<!--change the tuning parameter-->

## Illustration on simulated data

### 2024-05-31 paper.tex
Updated version for the discussion
Add error calculations

We define the function
\(z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}\).

For the \(i^{th}\) point,
\(z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(2)}_{jv})^2}\),
and assign it to \(H_h = \{i| z(i) = h\}\). Then, the fitted values for
\(i\) are defined as \(C_{h}^{(2)} = (c_{h1}, c_{h2})\).

@@

To assess how well our method captures and represents the underlying
structure of the \pD{} data, residuals are important. Residuals are
computed by taking the squared \pD{} Euclidean distance,
\(\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{hj})^2\).
Additionally, Mean Squared Error (MSE),
\(\frac{1}{n}\sum_{i = 1}^{n}\sum_{j = 1}^{p}(x_{ij} - C^{(p)}_{hj})^2\),
is computed based on residuals.

@@

\subsection{Illustration on simulated
data}\label{illustration-on-simulated-data}

>>>>

The fitted values refers to the \pD{} mappings of the \kD{} model.

@@

To assess how well our method captures and represents the underlying
structure of the \pD{} data, residuals are important. Residuals are
computed by taking the squared \pD{} Euclidean distance,
\(\sum_{h = 1}^{b}\sum_{i = 1}^{n_h}\sum_{j = 1}^{P} (x_{hij} - C^{(p)}_{hj})^2\).
Additionally, Mean Squared Error (MSE),
\(\frac{1}{n}\sum_{h = 1}^{b}\sum_{i = 1}^{n_h}\sum_{j = 1}^{P} (x_{hij} - C^{(p)}_{hj})^2\),
is computed based on residuals.

\subsection{Prediction}\label{prediction}

The prediction approach involves finding the nearest \kD{} model point
for a new \pD{} point. We define the function
\(z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}\), where
\(z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(p)}_{jv})^2}\)
maps each \pD{} point to its nearest \pD{} mapping of the model.
Therefore, the new observation \(i\) falls in the hexagon,
\(H_h = \{i| z(i) = h\}\) and the corresponding \kD{} bin centroids,
\(C_{h}^{(2)} = (c_{h1}, c_{h2})\) be the predicted values.

@@

\section{Deciding on the most suitable
fit}\label{deciding-on-the-most-suitable-fit}

\section{Illustration on simulated
data}\label{illustration-on-simulated-data}
